MaxEnt: What is it good for?

### 2015-08-10 ms.tex
COmpleted sentence

The reason for choosing a ``ragged'' distribution is to avoid making any
connection between MaxEnt and notions of smoothness or locality, since these
do not actually play a role.

>>>>

The reason for choosing a ``ragged'' distribution is to avoid making any
suggestion that MaxEnt relates to the ``smoothness'' of a distribution. The
entropy formula has no notion of certain hypotheses being neighbours of others.
I also chose the non-uniform prior to emphasise the role of MaxEnt as
a tool for updating probabilities, rather than assigning prior probabilities.
